Predictive 3D modelling of free oblique cutting introducing an ANN-based material flow law with experimental validation over a wide range of conditions

### 2023-12-10 Article.tex
Removal of "Preprint submitted to XX"
Revision-1

\journal{Journal}

@@

\author[1]{F. Ducobu\corref{cor1}}
\ead{Francois.Ducobu@umons.ac.be}
\cortext[cor1]{Corresponding author. Tel.: +32 65 45 68}

\author[2]{O. Pantal\'{e}}
\author[3]{B. Lauwers}

@@

A 3-axis GF Mikron VCE 600 Pro milling machine is used to perform dry orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper. As shown in Figure \ref{fig:ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample has 3 ribs of \qty{1}{\mm} width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} length. The test consists of removing the top layer (its height is the uncut chip thickness, $h$) of a rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (maximum value of \qty{40}{\metre\per\min}). The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample. Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To remove "Preprint submitted to Journal" at the bottom of the 1st page
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{}%
 \let\@evenfoot\@oddfoot}
\makeatother

\makeatletter
\def\ps@pprintTitle{
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \def\@oddfoot{\textit{\small{\hfill\today}}}
  \def\@evenfoot{\thepage\hfill}}
\makeatother

\journal{Journal}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author[1]{François Ducobu\corref{cor1}}
\ead{Francois.Ducobu@umons.ac.be}
\cortext[cor1]{Corresponding author. Tel.: +32 65 45 68}

\author[2]{Olivier Pantal\'{e}}
\author[3]{Bert Lauwers}

@@

A 3-axis GF Mikron VCE 600 Pro milling machine is used to perform dry orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper. As shown in Figure \ref{fig:ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample has 3 ribs of \qty{1}{\mm} width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} length. The test consists of removing the top layer (its height is the uncut chip thickness, $h$) of a rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (maximum value of \qty{40}{\metre\per\min}). The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample. Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times. \FD{Add comment to link with SECO's recommendations for the standard tool + reference}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statements \& Declarations}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\textbf{Funding}

\noindent The authors declare that this research received no external funding.\\

\noindent\textbf{Competing Interests}

\noindent The authors have no relevant financial or non-financial interests to disclose.\\

%\textbf{Availability of data and material}
%
%\textbf{Code availability}
%
%\textbf{Ethics approval and consent to participate}
%
%This article does not contain any studies with human participants or animals performed by any 
%authors.
%
%\textbf{Consent for publication}

\noindent\textbf{Author Contributions}

\noindent François Ducobu contributed to Data curation, Formal analysis, Investigation, Methodology, Software, Supervision, Validation, Visualization, Writing -- original draft and review \& editing (focussing on non ANN-related aspects). Olivier Pantalé contributed to Data curation, Formal analysis, Investigation, Methodology, Software, Validation, Visualization, Writing -- original draft and review \& editing (focussing on ANN-related aspects). Bert Lauwers contributed to Supervision and Writing -- review \& editing. All authors read and approved the final manuscript.
